Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex

We start by considering the distributions of MCC molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions from the combination of the three considered evolution stages. We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut \footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.}. of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
%
Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun,
whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

@@

\AP{let us recall to make the not about different molecular tracers also here}

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.

This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.

>>>>

We start by considering the distributions of MCC molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions from the combination of the three considered evolution stages. We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut\footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc (lower panels).
%
Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun,
whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

@@

\AP{let us recall to make the note about different molecular tracers also here}

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.

The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
are probably limited by the spatial resolution.
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
% 
This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.
